Guarded Recursion in Agda via Sized Types

### 2019-01-15 code-oneclock-paper/latex/Introduction.tex
Minor fixes in the text

However, the challenge lies in interpreting guarded recursion and guarded recursive types.
The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
This is a presheaf topos, whose objects are sets indexed by a natural number.
We use a slightly different approach: instead of natural numbers, we use sizes.
This means that the required interpretations need to be modified.

@@

\NW{Perhaps related work needs to be a separate section before conclusion. Alternatively, we can put it before the contributions (I think this is better)}

>>>>

In contrast, interpreting guarded recursion and guarded recursive types is more challenging.
The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
This is a presheaf topos, whose objects are sets indexed by a natural number.
We use a slightly different approach: instead of natural numbers, we use sizes.
This means that the required interpretations need to be modified.

@@

### 2019-01-15 code-oneclock-paper/latex/paper.tex
Rewrite in the text of fix
Minor fixes in the text

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
Now we got the simple type formers and their terms.
The next step is add the type formers required for guarded recursion.
We start by defining clock quantification and later, and how to construct terms of those types.
In addition, we define the fixpoint combinator.
We end this section by giving a type former for guarded recursive types.

>>>>

\input{Presheaves/Exp}

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
Now we have the simple type formers and their terms.
The next step is to add the type formers required for guarded recursion.
We start by defining clock quantification and the later modality, and how to construct terms of those types.
In addition, we define the fixpoint combinator.
We end this section by giving a type former for guarded recursive types.
